DeepSphere: a graph-based spherical CNN

### 2019-09-11 main.tex
Updates from Overleaf

\begin{table}
	\begin{tabular}{l|c c c c}
	\multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5}
	\multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
	\cite{jiang_spherical_2019} & 94.67 & - & - & -\\
	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h14m\\
	% 328'339
	\cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
	\cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
	% unknown
	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 & 25h \\
	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h35\\
	% 12'926'432
	\end{tabular}
	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
\end{table}

@@

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 & 25h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m
        % 590k
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

>>>>

\begin{table}
	\begin{tabular}{l|c c c c}
	\multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5}
	\multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
	\cite{jiang_spherical_2019} & 94.67 & - & - & -\\
	\cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h\\
	% 328'339
	\cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
	\cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
	% unknown
	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 33 & 13h \\
	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h\\
	% 12'926'432
	\end{tabular}
	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
\end{table}

@@

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m
        % 590k
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}
